% created on 2019-12-13
% @author : bmazoyer
\chapter*{Acknowledgements}

First and foremost, I want to thank my primary supervisor Dr Claude Comtat who believed in me and supported me every step of the way during my PhD project. I thank him for the patience he showed while discussing all my questions and ideas and his experience in guiding me throughout this project. Without ever applying pressure on me he has inspired me to deepen my knowledge and solidify my understanding of all involved concepts in our project.
 After these years working together, beyond the scientific values that he passed to me I have learned a lot about patience and being humble.

In addition, I want to thank my second supervisor Dr Simon Stute who provided me with the tools and technical knowledge to kick-off my project and also for sharing his vision of the CASToR tools with me and his more practical point of view of the research in the field.
With that, I want to also thank the CASToR collaboration and development team, particularly Dr Simon Stute, Dr Thibaut Merlin and Dr Marina Filipović. Without their previous work in developing and documenting these tools and their assistance in my developments and project work, this PhD project would not have been possible.

I want to thank my lab that hosted me during the last three and a half years, the former IMIV and current BioMaps laboratory of Paris Saclay. They provided a very friendly work environment and assisted with all the particular aspects of my project. I cannot list everyone from the lab here, but I would like to particularly express my gratitude to Dr Florent Besson for assisting with my project and sharing data and ideas on future projects. Also, I would like to thank Dr Florent Sureau who although joined the lab during the last few months of my project had a strong impact on my work and helped me by initiating interesting discussions on the project and by reviewing my work and this manuscript.

I would like to thank the Hybrid ITN project and partners, not only for selecting me and funding my project but also for providing me with unique opportunities to experience research in academia and industry as well as making me part of the Hybrid researcher community, which was and will be very useful in my professional development.

Beyond the professional life, moving to Paris and coping with the stress of the PhD life would not have been possible without the help of some exceptional friends that I have made here. Particularly George, George, George (in that order!) and Dimitris but also many many more that I can not mention due to limited space. Also, I would like to thank my friends from Greece and the UK who besides my absence are always close to me, and also my international friends from the Hybrid community.

Finally and above all I want to thank my family, my parents and brothers but also my extended big \mbox{(but not fat)} Greek family for their love and support throughout my journey. No more degrees, I promise!


