\chapter{Introduction}
Positron Emission Tomography (PET) has grown over a period of multiple decades from a tool used infrequently and primarily limited to research applications into a clinical imaging tool that plays a major role in many clinical practices and applications. 
In combination with multiple available radiotracers, the compounds that enable PET imaging to target and gather information of function at the molecular level, PET can provide unique biomarker information. The non-invasive nature of PET imaging, in combination with its potential for fully quantitative and reliable reproducibility of biomarker information, are some very important aspects that make it desirable in the delivery of precision medicine. Precision medicine is defined as an approach for disease treatment and prevention that takes into account individual variability in genes, environment, and lifestyle for each person. PET can play a vital role towards wider adoption of precision medicine due to its potential in the delivery of unique biomarker information~\cite{Subramaniam2017}.

Engineering advancements over the last decades have led to the development of highly efficient PET systems and in the creation of hybrid imaging systems, notably the PET/CT and PET/MR systems. The clinical need for multi-modality information has led to the fast adoption of such hybrid systems in clinical practice, with “one-stop-shop” protocols providing multi-modality information in single imaging sessions. Finally, hybrid systems have enabled the use of imaging information in “synergy”, to provide new and superior information on the underlying function and anatomy~\cite{Besson2020}.

Despite PET’s great success in clinical integration and applicability, the use of the modality and the main focus of many years of development have been concentrated on static imaging and qualitative or semi-quantitative measures. These have been driven mainly by applications in oncology, where these measures have so far been deemed sufficient in clinical pathways of cancer patients. At the same time, the ability of PET to provide fully quantitative measures of the biological functions under study has been reserved for research orientated applications and developments of new tracers or study of human physiology. 
But recently, the increasing focus on precision medicine has led to renewed attention to PET’s dynamic capabilities, for quantification of biologically relevant parameters by monitoring tracer kinetics and dynamic behaviour. These quantitative capabilities of PET are expected to be at the centre of future developments and clinical research for the next decade~\cite{Lammertsma2017,Meikle2021}.

\subsection*{Problemata}
The majority of the current clinical applications of PET can be found in oncology, where imaging information over the \gls{wb} is needed to detect and characterise the primary and metastatic disease. 
Whole body information is also desirable for many current and potential future applications of dynamic PET, which can result in fully quantitative measures and biomarkers information over the whole body. Beyond the use of such information for precision oncology, it can be used to study the kinetics of drugs distribution and function over the whole body.
This information can be used, while considering the human body as a single system, in the study of interactions and signalling between organs of the body to investigate complex physiology and pathology interactions~\cite{Meikle2021,Slart2021}.

A major limitation in the acquisition of the required PET data over the whole body is the limited axial field of view (A-FOV) of the majority of current clinical systems. The majority of the PET systems provide an axial coverage between 15 and 26 cm ~\cite{Vandenberghe2020}. 
In practice, whole-body coverage is achieved using multiple bed positions at different axial locations to provide the desired axial coverage~\cite{Schubert1996}, or via continuous axial bed motion (CBM) during the acquisition~\cite{Panin2014}. 
Both acquisition strategies can be extended for \gls{dwb} acquisition, by use of multiple repeated whole-body passes~\cite {Karakatsanis2011,Karakatsanis2013,Rahmim2019}.
Recently these \gls{dwb} protocols have been integrated within commercial PET systems~\cite{Hu2020}. 
These acquisition protocols pose challenges that arise from the resulting temporal gaps in the acquired dynamic data of any given bed position. These gaps are introduced at each bed position by the time spent on imaging other bed positions and by scanner system delays due to the time required to translate the bed in the axial direction and prepare for the acquisition of the next WB pass. The result is a sharp reduction in both total counts collected for each axial location as well as in temporal sampling frequency. Furthermore, acquisition of information from fast temporal changes in the early phase of the dynamic study is compromised, as those are not sampled adequately for all bed positions. Consequently, parameter estimates from dynamic whole-body PET acquisitions are potentially compromised by the above limitations in the acquisition, degrading their precision and accuracy.

Recently, scanners with increased A-FOV have been developed, offering increased sensitivity and substantially more or total-body coverage, that enables synchronous dynamic imaging of the whole body without the need of multiple bed positions and the associated issues with temporal gaps~\cite{Karp2020,Siegel2020, Cherry2018}.
These systems are currently found in very few pilot PET centres around the world and are not widely adopted in clinics yet. Since the first Total-Body scanner came online there has been an increased focus in the research for clinical applications of such systems, one of which is the use for dynamic whole-body imaging. As such the research interest in this field is expected to increase in the next years, with a particular focus on clinical utility as well as practical aspects of ease-of-use and cost-effectiveness.

\subsection*{Challenges and Contributions}
PET dynamic data can be used to extract kinetic parameters over regions of interest or on the voxel level, with the latter being used to create parametric images of the applied dynamic model.
Parametric images can provide information that is helpful in identifying and separating out different regions that exhibit different dynamic behaviour, without imposing predefined Volumes Of Interest (VOIs) in the analysis~\cite{Gallezot2019}.  
One of the major challenges in dynamic whole-body acquisitions using multiple whole-body passes is the estimation of accurate parametric images. Generation of parametric images from dynamic data requires fitting of the dynamic model of interest on time activity curves (TAC) for every voxel in the image. But due to the poor statistics and high noise associated with TAC measurements at the voxel level, which are further degraded by \gls{dwb} acquisition protocols, parametric image estimates can be heavily corrupted by noise and potentially biased. 
The main objective of this thesis was to explore acquisition optimization and novel reconstruction strategies for the improvement of whole-body parametric maps. 
The contributions can be separated into two major parts. The first part A) is focused on optimization of the \gls{dwb} protocol on a clinical PET/MR scanner, aiming at the reduction of temporal gaps in the DWB acquisition and increase of collected counts as well as an increase of sampling frequency. The second part B) is focused on the improvement in the use of acquired \gls{dwb} PET data by exploiting dynamic reconstruction algorithms. As part of this PhD project, various dynamic reconstruction algorithms were implemented in the open source reconstruction platform CASToR, for use with simulated and real data acquired from clinical scanners. An innovative approach for direct multi-bed dynamic reconstruction was developed and applied on real \gls{dwb} data, for the direct reconstruction of parametric images and temporal regularisation of the reconstructed activity image data.

\subsection*{HYBRID-ITN}
\input{1_Introduction/1_2_HYBRID}

\subsection*{Organization of the manuscript}
The manuscript is organised into two major parts. \textbf{Part \RNum{1}} outlines the methodologies involved in this project that are necessary for the understanding of the work carried out in this project. It is separated into four chapters which cover PET physics, pharmacokinetics, PET image reconstruction theory and implementations in custom software respectively. \textbf{Part \RNum{2}} of the manuscript provides the contributions made in this thesis in the form of four chapters.

Chapter~\ref{Chap3_1:AcquisitionOptimization} describes the development of a custom fully-automated protocol for dynamic whole body imaging on the Signa PET/MR and shows results from the use of this protocol on a \gls{nhp} scan.

Chapter~\ref{Chap3_2:SimStudy} describes the development and implementation of dynamic reconstruction methods within an open-source reconstruction software, which were subsequently used in this project, for dynamic single bed studies. The rest of the chapter outlines in detail an extensive simulation study conducted for the evaluation of the developed reconstruction methods for DWB Patlak parametric imaging. This simulation study was presented at the \textbf{IEEE/MIC} 2019 conference and submitted for publication to the~\textbf{Physics in Medicine \& Biology} journal. 

Chapter~\ref{Chap3_3:IsotoPK} presents the development of a direct multi-bed dynamic reconstruction method, as an extension of the developments presented in chapter~\ref{Chap3_2:SimStudy} for use with all dynamic bed data from DWB studies. In this chapter we present the application of this direct multi-bed reconstruction method to dynamic whole body data from a first in man pharmacological study conducted at our centre. The results of this application in the pharmacological study were presented at the \textbf{European Association of Nuclear Medicine} 2020 conference.

Chapter~\ref{Chap3_4:Residual} presents work conducted for the application of an adaptive modelling method for dynamic reconstruction and its application on whole body dynamic data from the pharmacological study presented in the previous chapter. The results of the application were presented at the \textbf{IEEE/MIC} 2020 conference.

A Conclusions and Prospects section is provided at the end of \textbf{Part \RNum{2}}, summarising the contributions in the context of the aims of this PhD project and with clinical utility of findings. Future prospects and aspects that need to be addressed further as also discussed.

Appendixes with supplementary material relating to the presented work are also provided.

Secondary contributions made in collaboration projects as part of the ITN programme are provided at the end of the manuscript in the \textbf{Secondary Contributions} section.