%\section{Introduction}
As shown previously in multiple applications in the literature, dynamic reconstruction can improve activity and parametric image estimates by making use of dynamic models directly in the reconstruction process, resulting in more accurate modelling of the noise from the raw PET data~\cite{Reader2014}. 

In this chapter, we shortly describe the implementation of a dynamic reconstruction framework and dynamic reconstruction functionalities in CASToR. A fraction of this PhD project was focused on the development and validation of these functionalities that were necessary to achieve the project aims. The developments were conducted in collaboration with other CASToR developers, mainly with Dr Thibaut Merlin, Dr Simon Stute and Dr Marina Filipović.
In addition, dynamic functionalities were implemented within a generic framework that allows for future expansion and contributions by developers of CASToR, to include more dynamic models and enable more complex and higher dimensional modelling (eg. dynamic and respiratory "5D" modelling , etc.).

In the remaining of this chapter, we present work conducted with simulated and real data on the use and respective benefits of various dynamic reconstruction strategies for DWB parametric imaging. This study has been submitted to the journal of \textbf{Physics in Medicine \& Biology} for review in May 2021. 

\input{3_Results/3_2_Dynamic_Reconstruction_SimulationStudy/GAP_STUDY_IOP}

\section{Conclusions to this Chapter}
Dynamic reconstruction capabilities were successfully developed and validated in CASToR, for multiple dynamic models and optimization algorithms. Along with dynamic developments for a PET analytical simulator, those tools have enabled an extensive evaluation of dynamic reconstruction methods for application in DWB imaging. The developed tools were used for the application of dynamic reconstruction on real data and were further evaluated and expanded, in the work that is described in the following chapter, for real DWB data.